\documentclass[10pt,aspectratio=169]{beamer}
\beamertemplatenavigationsymbolsempty
\usepackage{graphicx}
\usepackage{amsmath}
\usetheme{default}

\begin{document}
\begin{frame}
  
\end{frame}

\begin{frame}
  \frametitle{What are we solving?}
  \begin{itemize}
    \item A system of 1D transport equations for tokamak plasmas.
    \item Evolves profiles of:
    \begin{itemize}
        \item Ion Temperature ($T_i$)
        \item Electron Temperature ($T_e$)
        \item Electron Density ($n_e$)
        \item Poloidal magnetic flux ($\psi$)
    \end{itemize}
    \item Self-consistently calculates:
    \begin{itemize}
        \item Plasma geometry
        \item Bootstrap current
        \item Conductivity
        \item Heating and particle sources
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Numerical Scheme}
  \begin{itemize}
    \item \textbf{PDEs:} 1D (in $\rho$) coupled, nonlinear, second-order parabolic transport equations.
    \item \textbf{Spatial Discretization:} Finite Volume Method on a staggered grid.
    \begin{itemize}
        \item Diffusion: Central differencing.
        \item Convection: Upwind scheme with a Peclet number-dependent flux limiter.
    \end{itemize}
    \item \textbf{Boundary Conditions:}
    \begin{itemize}
        \item Core ($\rho=0$): Zero-gradient (Neumann).
        \item Edge ($\rho=1$): Fixed value (Dirichlet).
    \end{itemize}
    \item \textbf{Time Stepping:} Fully implicit backward Euler method.
    \begin{itemize}
        \item A predictor-corrector or Newton-Raphson method solves the nonlinear system.
    \end{itemize}
    \item \textbf{Coefficients \& Sources:} Self-consistently calculated from physics models (e.g., QLKNN, Sauter).
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Core Physics Models}
  \begin{itemize}
    \item \textbf{Plasma Geometry:} The magnetic equilibrium (the shape of the nested magnetic surfaces) is determined by the plasma pressure and the total current profile. It is recalculated as the profiles evolve to maintain consistency.
    \item \textbf{Bootstrap Current:} A self-generated current driven by the plasma's pressure gradient in the toroidal geometry. It is essential for achieving efficient, steady-state operation in a reactor.
    \item \textbf{Conductivity:} The plasma's ability to carry current, which is the inverse of resistivity. It depends strongly on the electron temperature and the amount of impurities in the plasma ($Z_{eff}$).
    \item \textbf{Heating and Particle Sources:} These are user-defined profiles that model the injection of energy (e.g., from neutral beams or radio-frequency waves) and particles (e.g., from gas puffing) that sustain the plasma.
  \end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]
  \bibliographystyle{abbrv}
  \bibliography{main}
  \nocite{*}
\end{frame}

\end{document}
